\thesistitle

### 2019-07-19 sections/conclusion.tex
Type 4 clones

\subsection{Identifying more types/definitions for clones}

@@

\subsection{Running our experiments with a greater diversity of software projects}

>>>>

\subsection{Identifying more types/definitions for clones}
In this study, we proposed a set of clone type definitions for which a refactoring opportunity is known. We based these clone type definitions on the clone type definitions that are commonly used in literature. The design of these clone type definitions entailed some decisions that have a large impact on the clones we considered for refactoring in this study.

Choosing different

\subsubsection{Type 4 clones}
In section \ref{chap:backgroundclonetypes} we introduced the clone types that are used in literature. Of these clone types, we considered type 1, 2 and 3 for refactoring. We chose not to consider type 4 clones because they appear far less in source code and are more difficult to detect and refactor. However, that does not mean that these clones should not be refactored.

We think that there are relevant research opportunities in refactoring type 4 clones. Type 4 clones are functionally equal pieces of code that are implemented through different implementations. Although functionally equal, type 4 clones might still differ in other aspects. For instance, for type 4 clones, one alternative might be easier to maintain. Also, they can differ (significantly) in performance.

There are interesting research opportunities in automatically choosing the better alternative among type 4 clone instances.

@@

\subsection{Running our experiments with a greater diversity of software projects}
Currently

\subsection{Automatically refactoring code that is duplicated with a library}
